\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-28 syntax.tex
minor

Next we talk about inheritance judgement. Note that, there will be a lot of $\sigma_1, A_1$ and $\sigma_2, A_2$, and in these cases, $A_1$ is the result of the sealing of $\sigma_1$, i.e. we assume we have a term $\goodSeal{\Gamma}{f_1}{\sigma_1}{A_1}$, $\goodSeal{\Gamma}{f_2}{\sigma_2}{A_2}$ in the premises of judgements when needed.

@@

Inheritance are
judgement so naturally second class citizen data (i.e. not something
function can return and cannot be assigned to variables), and it looks
very much like a function that transform a given linkage. Similar to plugin implementation and \ruleref{Lnkg Add}, we resolve \ref{chg:consistency} by making sure corresponding fields are in corresponding context during inheritance, and thus an overriding term can only refer to fields before the overriden field.

@@

"inhinh" is special because it requires user to provide a proof of
``upcasting'' from the context of the child to that of the parent.
In other words, if I want to inherit a specific field from the parent, I
have to convince the type checker that my current context can
``accommodate'' the inherited field.

Override "inhov" is even more special because in mundane OO programming language, we usually require that the overriding term has the same type/interface as the overriden one.  Here we don't since the very reason we want the same type/interface is that we hope other inherited fields can use this overridden/late-binding field without breaking abstraction, and this reason is already managed by the premises of "inhinh", the upcasting proof $\uparrow^s$. Thus "inhov" is quite like "inhext", where overriding is just throwing away one parent field. This difference also show one of the distinct feature of our vanilla family inheritance compared to the mainstream OO inheritance---family inheritance don't need to introduce the concept of ``subclassing'' between families and thus no bounded polymorphism yet\footnote{Of course once trait and interface comes in, we can have bounded polymorphism back}, and code reuse is mainly achieved by late binding. Without ``subclassing'', there is no way of confusing inheritance and subtyping. Note that, "inhov" is also responsible for ``extending'' inductive type---the extended inductive type directly override the old ones when using metatheory to program, just like how plugin implementation works.

>>>>

Next we talk about inheritance judgements. Note that, there will be a lot
of $\sigma_1, A_1$ and $\sigma_2, A_2$, and in these cases, $A_1$ is the
result of the sealing of $\sigma_1$, i.e. we assume we have a term
$\goodSeal{\Gamma}{f_1}{\sigma_1}{A_1}$,
$\goodSeal{\Gamma}{f_2}{\sigma_2}{A_2}$ in the premises of judgements
when needed.

@@

Inheritance are judgements so naturally second class citizen data (i.e.,
not something function can return and cannot be assigned to variables),
and it looks very much like a function that transforms a given linkage.
Similar to plugin implementation and \ruleref{Lnkg Add}, we resolve
\ref{chg:consistency} by making sure that a derived family preserves the
ordering of fields in its base family:
in an inheritance judgment, an overriding term is checked in a context
that contains those fields preceding it in the base family.

@@

"inhinh" is special because it requires the user to provide a proof of
``upcasting'' from the context of the child to that of the parent.
In other words, if I want to inherit a specific field from the parent, I
have to convince the type checker that my current context can
``accommodate'' the inherited field.

Override "inhov" is even more special because in mundane OO programming
language, we usually require that the overriding term has the same
type/interface as the overriden one.  Here we don't since the very
reason we want the same type/interface is that we hope other inherited
fields can use this overridden/late-binding field without breaking
abstraction, and this reason is already managed by the premises of
"inhinh", the upcasting proof $\uparrow^s$. Thus "inhov" is quite like
"inhext", where overriding is just throwing away one parent field. This
difference also shows one of the distinct features of our vanilla family
inheritance compared to the mainstream OO inheritance---family
inheritance need not introduce the concept of ``subclassing''
between families and thus no bounded polymorphism yet\footnote{Of course
once trait and interface comes in, we can have bounded polymorphism
back}, and code reuse is mainly achieved by late binding. Without
``subclassing'', there is no way of confusing inheritance and subtyping.
Note that, "inhov" is also responsible for ``extending'' inductive
types---an extended inductive type directly overrides the old one when
using metatheory to program, just like how plugin implementation works.
